Figures

### 2020-11-14 manuscript/_main.Rmd
Edits: figures Rmd file

@@

>>>>

---
title: "Figures"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework of generating theoretical branching river networks. Branching river networks are dipicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example). Environmental conditions at headwaters (i.e., the most upstream patches) are generated randomly as a realization of a normal distribution and propagate downstream with local environmental noises (a spatially autoregressive process with a white noise; Methods). Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values). (B) Example of intesively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C). Red dots indicate sampling sites for fish surveys. (C) Map of study regions (left, Midwest, US; right, Hokkaido, Japan). Watersheds (i.e., metacommunities) are gray-shaded in propotion to the number of sampling sites."}

source(normalizePath("../empirical/figure_map.R"))

\newpage

```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different compeition strength. Competitive coefficients ($\\alpha_{c}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). In this simulation, environmental vairiability among headwaters (i.e., the most upstream patches), which is expressed as the standard deviation of a normal distribution ($\\sigma_{h} = 1.0$), was greater than that of local environmental noises occurring at each habitat patch ($\\sigma_{l} = 0.01$). Dispersal probability $p_{d}$ was 0.01 for all the scenarios."}

source(normalizePath("../theory/figure_n_patch.R"))
```

\newpage

```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. See Figure 2 for details."}

source(normalizePath("../theory/figure_p_branch.R"))
```

\newpage

```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions. Dots represent watershed replicates (i.e., metacommunities) and lines are predicted values from the linear regression models."}

source(normalizePath("../empirical/figure_diversity.R"))
```

<!--chapter:end:figures.Rmd-->

@@

<!--chapter:end:manuscript.Rmd-->

---
title: "Tables"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

  knitr::opts_knit$set(root.dir = here::here("empirical"))

```{r, echo = FALSE, message=FALSE, results='asis'}

source(normalizePath("../empirical/analysis_lm.R"))

stargazer::stargazer(m_alpha$model, m_beta$model, m_gamma$model,
                     header = FALSE,
                     title = "Estimated parameters of robust linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions. Dependent variables were log-10 transformed. Environmental variables (air temperature, precipitation, logit \\% forest) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one.",
                     type = "latex",
                     ci = TRUE,
                     covariate.labels = c("$log_{10}$ Watershed area",
                                          "$log_{10}$ Branching probability",
                                          "Region (Midwest vs. Hokkaido)",
                                          "Air temperature",
                                          "Precipitation",
                                          "Logit \\% forest",
                                          "Intercept"),
                     single.row = FALSE,
                     digits = 2,
                     dep.var.labels.include = FALSE,
                     column.labels = c("$\\alpha$ richness", "$\\beta$ richness", "$\\gamma$ richness"),
                     keep.stat = c("rsq"),
                     model.numbers = FALSE)

<!--chapter:end:table.Rmd-->

### 2020-11-14 manuscript/figures.Rmd
Edits: figures Rmd file

```{r, fig.height=7, fig.width=8, fig.cap="(A) Example of theoretical branching river networks. Branching river networks are dipicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example). Environmental conditions at the headwaters (the most upstream patches) are generated randomly and propagate downstream with local noises. Habitat patches are colored in proportion to environmental values (similarly-colored habitat patches have similar environmental values). (B) Map of study regions (left, Midwest, US; right, Hokkaido, Japan). Watersheds (i.e., metacommunities) are colored in propotion to the number of sites for fish surveys."}

@@

```{r, fig.height=5, fig.width=7}

source(normalizePath("../theory/figure_n_patch.R"))

@@

```{r, fig.height=5, fig.width=7}

source(normalizePath("../theory/figure_p_branch.R"))

@@

```{r, fig.height=6, fig.width=8}

source(normalizePath("../empirical/figure_diversity.R"))

>>>>

```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks. Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example). Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods). Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values). (B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C). Red dots indicate sampling sites for fish surveys. (C) Map of study regions (left, Midwest, US; right, Hokkaido, Japan). Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}

@@

```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{c}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). In this simulation, environmental variability among headwaters (i.e., the most upstream patches), which is expressed as the standard deviation of a normal distribution ($\\sigma_{h} = 1.0$), was greater than that of local environmental noise occurring at each habitat patch ($\\sigma_{l} = 0.01$). Dispersal probability $p_{d}$ was 0.01 for all the scenarios."}

source(normalizePath("../theory/figure_n_patch.R"))
```

@@

```{r, fig.height=6, fig.width=8, fig.cap="Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. Lines and shades are loess curves fitted to simulated data and its 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. See Figure 2 for details."}

source(normalizePath("../theory/figure_p_branch.R"))
```

@@

```{r, fig.height=6, fig.width=8, fig.cap="Influences of ecosystem size (A, watershed area) and complexity (B, branching probability) on $\\alpha$ (left), $\\beta$ (middle), and $\\gamma$ diversity (right) in Hokkaido and Midwest regions. Dots represent watershed replicates (i.e., metacommunities), and lines are predicted values from the linear regression models."}

source(normalizePath("../empirical/figure_diversity.R"))
```
